\documentclass[]{article}

  \input{includes/header}

  \fancyhead[L]{\fontsize{12}{20}\sc joachim vandekerckhove}
  \definecolor{primaryColor}{rgb}{.5,.0,.0}
  \definecolor{secondaryColor}{rgb}{.5,.5,.5}


\begin{document}

\vspace{1ex}\null

\subsection*{Contact information}

    Department of Cognitive Sciences\\
    2324 Social and Behavioral Sciences Gateway Building (SBSG)\\
    University of California, Irvine\\
    Irvine, CA 92697-5100\\[1ex]
    \indent\indent Phone: +1 (949) 824-5958\\
    \indent\indent joachim@uci.edu\\
    \indent\indent \url{www.cidlab.com}
    
\subsection*{Employment history}
\slist
  2016 -- present & \textbf{Associate Professor}, Department of Cognitive Sciences \\ 
                  & University of California, Irvine \\
  2015 -- present & \textbf{Affiliated Faculty}, Department of Statistics\\
                  & University of California, Irvine \\
  2011 -- present & \textbf{Affiliated Faculty}, Institute for Mathematical Behavioral Sciences\\
                  & University of California, Irvine \\
  2011 -- 2016    & \textbf{Assistant Professor}, Department of Cognitive Sciences \\ 
                  & University of California, Irvine \\
  2011 -- present & \textbf{Research Fellow}, Faculty of Psychology and Educational Sciences\\ 
                  & University of Leuven, Belgium \\
  2010 -- 2012    & \textbf{Post-Doctoral Fellow} \\
                  & Research Foundation---Flanders (FWO) \\
  2009 -- 2010    & \textbf{Post-Doctoral Research Associate}, Faculty of Medicine\\
                  & University of Leuven, Belgium \\
\elist

\subsection*{Education}
\slist
  2005 -- 2009 & PhD in Quantitative Psychology and Psychometrics \\ 
               & University of Leuven, Belgium\\
  2002 -- 2005 & Master in Psychology (Licentiate)\\
  			   & University of Leuven, Belgium\\
  2000 -- 2002 & Bachelor in Psychology (Candidate)\\
               & University of Leuven, Belgium\\	
\elist

\subsection*{Professional memberships (past and present)}
\scolsz
  Fellow of the Psychonomic Society\\
  Member of the Society for Mathematical Psychology\\
  Member of the Psychometric Society\\
  Member of the European Society for Cognitive Psychology\\
  Member of the International Society for Research in Emotion\\
  Member of the American Statistical Association
\ecolsz

\newpage

\section*{Research}
\subsection*{Research interests}
\scolss
   Stochastic process models & Computational modeling of cognition\\
   Bayesian statistics       & Computational methods \\
   Individual differences    & Psychometrics         \\
   Integrative modeling      & Data fusion\\
   Robust science            & Meta-analysis
\ecolss

\subsection*{Extramural grants}
\slist
  June 2021      & National Science Foundation grant \#2051186:
  			  	   ``Exploratory and confirmatory neurocognitive modeling with latent variables.'' 
                   36 months.  
                   Role: \textbf{Principal Investigator} (with R.~Srinivasan).
                   \$349,551.00\\
  September 2019 & National Science Foundation grant \#1850849:
  			  	   ``Critical tests of neurocognitive relationships.''  
                   36 months.  
                   Role: \textbf{Principal Investigator} (with R.~Srinivasan).
                   \$674,807.00\\
  February 2018  & National Science Foundation grant \#1754205:
  			  	   ``RR: Workshop on Robust Social and Behavioral 
                   Sciences.''  
                   12 months.  
                   Role: \textbf{Principal Investigator} (with M.~D.~Lee).
                   \$62,391.00\\
  April 2017     & National Science Foundation grant \#1658303:
  			  	   ``Estimation of unidentified cognitive models 
                   with physiological data.''  
                   24 months.  
                   Role: \textbf{Principal Investigator} (with R.~Srinivasan).
                   \$337,028.00\\
  April 2016     & National Science Foundation: Graduate Research
  				   Fellowship Award (DGE-1321846; Awarded to advisee
                   Alexander Etz).  
                   36 months.  
                   Role: \textbf{Adviser}.
                   \$132,000.00\\
  January 2016   & William K. and Katherine W. Estes Fund
  				   (Psychonomic Society and Association for
                   Psychological Science): ``Summer school for
                   computational cognitive modeling''.  
                   Role: \textbf{Contributor} (with S.~Lewandowsky and 
                   K.~Oberauer).
                   \$15,000.00\\
  September 2015 & National Science Foundation grant \#1534472:
  				   ``Bayesian methods for meta-analysis in the
                   presence of publication bias.''  
                   36 months. 
                   Role: \textbf{Principal Investigator.}  
                   \$260,000.00\\
  July 2015      & European Society for Cognitive Psychology:
  				   ``Summer school for computational cognitive
                   modeling''.  
                   Role: \textbf{Contributor} (with S.~Lewandowsky and 
                   K.~Oberauer).
                   \$22,000.00\\
  July 2015      & National Science Foundation: ``Support for the
  				   Applications of Mathematical Psychology to
                   Industry meeting''. 
                   Role: \textbf{Organizer} (with J.~Trueblood). 
                   \$5,000.00\\
  June 2014      & John Templeton Foundation grant \#48192: ``A
  				   formal modeling framework for the dynamics of
                   subjective well-being.''  
                   36 months.  
                   Role: \textbf{Principal Investigator.}  
                   \$540,018.00\\
  April 2014     & National Science Foundation: Graduate Research
  				   Fellowship Award (DGE-1321846; Awarded to advisee
                   Maime Guan).  
                   36 months.  
                   Role: \textbf{Adviser.}
                   \$121,500.00\\
  February 2014  & Volkswagen Foundation teaching grant: ``Summer
  				   school for computational cognitive modeling''. 
                   Role: \textbf{Contributor.} (with S.~Lewandowsky and 
                   K.~Oberauer). 
                   \$70,000.00\\
  September 2012 & National Science Foundation grant \#1230118:
  				   ``Cognitive structural equation models.''  
                   36 months.  
                   Role: \textbf{Principal Investigator.}
                   \$250,000.00\\
  October 2010   & Research Foundation---Flanders postdoctoral
  				   research grant: ``Dynamic cognitive psychometrics.'' 
                   36 months.  
                   \$200,000.00\\
%  August 2010    & Research Foundation---Flanders (FWO) travel
%  				   grant: ``Fitting a self-regulating accumulator
%                   model of human decision-making''.  
%                   \$3,000.00\\
  October 2009   & University of Leuven Research Council
  				   postdoctoral research grant: ``A statistical
                   framework for Approximate Bayesian Computation.''
                   12 months.  
                   \$65,000.00\\
%  September 2008 & Research Foundation---Flanders (FWO) travel
%  			       grant: ``A Bayesian treatment of the LATER model
%                   for simple response times''. 
%                   \$2,500.00\\
%  November 2007  & Research Foundation---Flanders (FWO) travel
%  				   grant: ``Hierarchical diffusion models for 
%                   two-choice response times''.  
%                   \$3,000.00
\\[4ex]
\elist

\subsection*{Intramural grants}
\slist
  July 2015      & UC Irvine School of Social Sciences Office of the
  				   Dean: ``Support for the Applications of
                   Mathematical Psychology to Industry meeting''.
                   Role: Organizer. 
                   \$3,000.00\\
  July 2015      & UC Irvine School of Social Sciences Office of
  				   Graduate Affairs: ``Support for the 48th Meeting
                   of the Society for Mathematical Psychology''. 
                   Role: Principal organizer (with J. Trueblood).
                   \$3,000.00\\
  July 2015      & UC Irvine Department of Cognitive Sciences:
  				   ``Support for the 48th Meeting of the Society for
                   Mathematical Psychology''.  
                   Role: Principal organizer (with J. Trueblood). 
                   \$2,500.00\\
% July 2015      & UC Irvine Department of Cognitive Sciences:
%  				   ``Consistency of Muscle Test Results''. 
%                  Role: Adviser (with J. Wilson).  
%                  \$250.00\\
% July 2015      & UC Irvine Undergraduate Research Opportunity
%  				   Program (UROP): ``Consistency of Muscle Test 
%                  Results''. 
%                  Role: Adviser (with J. Wilson).
%                  \$700.00\\
  November 2012  & UC Irvine School of Social Sciences:
  				   ``Interfacing Models with Brain Signals to
                   Investigate Cognition''. 
                   Role: Co- Principal Investigator (with 
                   R. Srinivasan, and J. Krichmar).
                   \$4,000.00\\
  June 2012      & UC Irvine Summer Undergraduate Research Program
  				   (SURP): ``Publication Bias in Three Prominent
                   Psychological Journals''. 
                   Role: Adviser (with M. Guan).
                   \$2,000.00\\
\elist

\subsection*{Professional recognitions}
\slist
  July 2020      & UC Irvine School of Social Sciences Outstanding Teaching Award (Spring 2020)\\
  December 2016  & UC Irvine Social Science Assistant Professor Research Award (\$5,000)\\
  December 2016  & My student Beth Baribault won the \textit{Berkeley
  				   Initiative for Transparency in the Social
                   Sciences'} Leamer-Rosenthal Prize for Open 
                   Social Science for her work under my supervision (\$10,000)\\
  September 2015 & UC Irvine School of Social Sciences Outstanding Teaching Award (Spring 2015)\\
  July 2014      & \textit{Society for Mathematical Psychology}'s 
                   William K. Estes Early Career Award (\$1,250)\\
\elist

\newcommand{\vdkh}{\textbf{Vandekerckhove, J.}}

\subsection*{Recent talks}
\srefs
\i \vdkh{} (2018, September).
\newblock \textit{Cognitive psychometrics for multimodal data.}
\newblock Invited presentation at the Second Summer School on Statistical Methods for Linguistics and Psychology, Potsdam, Germany.

\i \vdkh{} (2018, July).
\newblock \textit{Robust tests of theory with randomly sampled experiments.}
\newblock Annual Meeting of the Society for Mathematical Psychology, Madison, WI

\i \vdkh{} (2017, November).
\newblock \textit{Publication bias and statistical evidence in the psychological literature.}
\newblock Annual Meeting of the Psychonomic Society, Vancouver, Canada.

\i \vdkh{} (2017, September).
\newblock \textit{Some Bayesian and psychometric thoughts on the reproducibility crisis.}
\newblock Invited presentation at the Stanford Cognitive Sciences seminar.

\i \vdkh{} (2017, March).
\newblock \textit{Statistical power and evidence in the psychological literature.}
\newblock Invited presentation at the Arthur M.\ Sackler Colloquium of the National Academy of Sciences. Washington, DC.

\i \vdkh{} (2017, February).
\newblock \textit{Mitigation of publication bias with behavioral process models.}
\newblock Annual Interdisciplinary Conference. Breckenridge, CO.

\erefs


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% PUBLICATIONS %%%%%%%%%
   \input{publications.tex}
   
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection*{Software}
\srefs
\i \vdkh{} (2020).
\newblock MathPsych Virtual [Website, software, and manual]. An online conference venue for events organized by the Society for Mathematical Psychology.
\newblock Available via \url{mathpsych.org}
  
\i \vdkh{} (2017).
\newblock Build-A-Bayes [Educational online app].
\newblock Available via \url{osf.io/mvp53}

\i \vdkh{} (2015).
\newblock Trinity [Software and manual].
\newblock Available via \url{sw.cidlab.com}

\i Wabersich, D., Lee, M. D., \& \vdkh{} (2013).
\newblock jags-alcove [Software and manual].
\newblock Available via \url{sw.cidlab.com}

\i Wabersich, D., \& \vdkh{} (2013).
\newblock jags-wiener [Software and manual].
\newblock Available via \url{sw.cidlab.com}

\i Wabersich, D., Lee, M. D., \& \vdkh{} (2013).
\newblock RAlcove [Software and manual].
\newblock Available via \url{sw.cidlab.com}

\i Wabersich, D., Lee, M. D., \& \vdkh{} (2013).
\newblock RWiener [Software and manual].
\newblock Available via \url{sw.cidlab.com}

\i Oravecz, Z., Tuerlinckx, F., \& \vdkh{} (2012). 
\newblock BHOUM: Bayesian Hierarchical Ornstein-Uhlenbeck Modeling [Software and manual]. 
\newblock Available via \url{bayesian.zitaoravecz.net}

\i Oravecz, Z., \vdkh{}, \& Batchelder, W. H. (2012).
\newblock Bayesian Cultural Consensus Toolbox [Software and manual]. 
\newblock Available via \url{bayesian.zitaoravecz.net}

\i \vdkh{}, \& Tuerlinckx, F. (2009). 
\newblock wiener.odc and wienereta.odc [Software and manual]. 
\newblock Available via \url{sw.cidlab.com}

\i \vdkh{}, \& Tuerlinckx, F. (2007). 
\newblock The Diffusion Model Analysis Toolbox [Software and manual].
\newblock Available from \url{sw.cidlab.com}

\i \vdkh{} (2006).
\newblock General simulated annealing algorithm.
\newblock Available via \url{sw.cidlab.com}
\erefs


\subsection*{Dissertation}
\srefs
\i \vdkh{} (2009).
\newblock  Extensions and applications of the diffusion model for two-choice response times. Unpublished doctoral dissertation. 
\erefs

\subsection*{Other publications}
\srefs
\i \vdkh{} (2019, December).   \newblock Freedom of choice vs.\ undisclosed flexibility: Researcher degrees of freedom in model-based inference. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\i \vdkh{} (2019, September).  \newblock On being SMARTer than Vincent. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\i \vdkh{} (2019, August).     \newblock Detecting Bigfoot vs.\ brain waves: New approaches to multivariate data analysis. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\i \vdkh{} (2019, May).        \newblock You can obscure a lot by just plotting: Cognitive science of data presentation. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\i \vdkh{} (2019, February).   \newblock Weighting or besting? Speeded multi-attribute choice  [Original title: The weighting is the hardest part]. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\i \vdkh{} (2018, February).   \newblock From classical to new to real: A brief history of \#BayesInPsych. {\em Psychonomic Society Featured Content.}
\newblock Via \hyperlink{featuredcontent.psychonomic.org}{featuredcontent.psychonomic.org}
\erefs


\subsection*{Media}
\srefs
  \item[--] I maintain \textbf{cidlab.com} to distribute research results and publications; and various other websites to announce events and workshops.
  \item[--] My lab provides support for \textbf{The Bayes Factor}, a podcast on Bayesian inference and the people behind it.
  \item[--] My research has featured in numerous media outlets, including the \textit{New York Times}, \textit{National Public Radio}, the \textit{Chronicle of Higher Education}, \textit{WIRED Magazine}, \textit{Science News}, and \textit{Nature News}.
% \item[--] My work on the dynamics of subjective well-being was posted on the UCI News service and widely circulated, and my work on model complexity was featured on the Psychonomic Society's blog (\url{http://www.psychonomic.org/news/news.asp?id=316843}).
% \item[--] My advocacy for more robust science was mentioned by President Marcia McNutt of the National Academy of Sciences in a letter to the editor of the \textit{Chronicle of Higher Education} (\url{http://www.chronicle.com/blogs/letters/scientists-dont-view-reproducibility-as-risky-business/}).
\erefs
 
\Needspace{0.66\textheight}
\section*{Service}

\subsection*{Graduate advising}
\slist
2016 -- present & Alexander Etz    (chair)\\
2014 -- 2020    & Colin Kupitz     (chair)              --- now at Air Force Research Labs\\
2014 -- 2019    & Beth Baribault   (chair)              --- now at UC Berkeley \\
2013 -- 2019    & Maime Guan       (with M.~D.~Lee)     --- now at Apple, Inc. \\
2013 -- 2018    & Irina Danileiko  (with M.~D.~Lee)     --- now at Niantic, Inc. \\
2012 -- 2017    & Michael D.~Nunez (with R.~Srinivasan) --- now at UC Irvine
\elist

\subsection*{Other mentoring activities}
\slist
2017 -- 2019,   & \\
\hspace{0.5em} 2020 -- present & Assistant project scientist Michael D.~Nunez (with R.~Srinivasan)\\
2018            & Assistant project scientist Ravi Selker      (with M.~D.~Lee) \\
2016 -- 2017    & Visiting researcher Anna-Lena Schubert\\
2013 -- 2014    & Research specialist Dominik Wabersich
\elist

\subsection*{Departmental service}
\slist
2017 -- present    & Graduate Director of Cognitive Sciences\\
2017 -- present    & Chair of the Graduate Admissions Committee of Cognitive Sciences\\
2013 -- 2017       & Undergraduate Director of B.S. 
					 Cognitive Sciences\\
2012 -- present    & Academic personnel committee member (5) 
					 and chair (2)\\
2012 -- present    & Search committee member (4) and chair (2)\\
2011 -- present    & Doctoral committees (6), 
				     advancement committees (11),
                     concentration exams (8)
\elist


\subsection*{Other service}
\slist
2019 -- present    & \textbf{Conference Chair} of the Society for Mathematical Psychology\\
2019 -- present    & \textbf{Executive Board Member} (\emph{ex officio}) of the Society for Mathematical Psychology\\
2017 -- present    & \textbf{Representative} (elected) of the School of Social Sciences to the Senate Assembly\\
2017 -- present    & \textbf{Committee Member}, Faculty Advisory Committee for Research Cyberinfrastructure
\elist


\subsection*{UCI Teaching}
\slist
Undergraduate & Probability and Statistics in Psychology;
                Advanced experimental methods in psychology (lecture and lab);
                Honors advanced experimental methods in psychology (lecture and lab);
                Individual study \\
Graduate      & Algorithmic statistics;
                Bayesian inference;
                Computational statistics;
                Social data science;
                Software development;
                Transparent and reproducible science
\elist

\subsection*{External teaching}
\slist
September 2018 & \textbf{Invited lecturer}, Workshop at University of
			     Potsdam, ``Cognitive psychometrics for multimodal data''\\
September 2016 & \textbf{Invited lecturer}, Workshop at University of
			     Toronto, ``A practical course in Bayesian
                 graphical modeling'' (with M.~D.~Lee)\\
2010 -- 2016   & \textbf{Lecturer and co-organizer}, biennial 
			     Computational Cognitive Modeling summer school\\
March 2015     & \textbf{Invited lecturer}, seminar for Interdisciplinary
			     Data Sciences Consortium, University of South
                 Florida, Tampa, ``Cognitive psychometrics and
                 cognitive latent variable models''\\
July 2015      & \textbf{Invited lecturer}, Workshop at University of
			     Zurich, ``Cognitive psychometrics and cognitive
                 latent variable modeling''\\
December 2010  & \textbf{Invited lecturer}, University of Zurich doctoral
			 	 program, ``A practical course in Bayesian
                 graphical modeling'' (with M. D. Lee)\\
September 2010 & \textbf{Invited lecturer}, University of Zurich doctoral
				 program, ``Programming models in MATLAB''\\
2006 -- 2011   & \textbf{Teaching assistant} (2006 -- 2008, 2010 -- 2011),
				 substitute local coordinator (2007), and 
                 co-lecturer (2008) ``Socrates-Erasmus Intensive
                 Program on Mathematical and Computational Models in
                 the Psychological Sciences''\\
2005 -- 2008   & \textbf{Teaching assistant} and tutor for various
				 undergraduate courses on statistics. Co-lecturer
                 for undergraduate courses on mathematical modeling
\elist

\subsection*{Editorial and Ad-hoc reviewer service}
\slist
2020 -- present & \textbf{Associate editor}, \textit{Psychonomic Bulletin \& Review}\\
2018 -- 2019    & \textbf{Associate editor}, \textit{Psychonomic Society Digital Content}\\
2017 -- present & \textbf{Editorial board member}, \textit{Advances in Methods 
                  and Practices in Psychological Science}\\
2015 -- 2018    & \textbf{Guest lead editor}, 
 				  \textit{Psychonomic Bulletin \& Review}, Special
                  issue on statistical recommendations (with J.~N.~Rouder and J.~K.~Kruschke)\\
2016 -- 2018    & \textbf{Panelist}, \textit{National Science Foundation},
				  Advisory Panel for the Methodology, Measurement,
                  and Statistics (MMS) Program\\
2016 -- 2019    & \textbf{Consulting editor}, 
			      \textit{Behavior Research Methods}\\
2016 -- 2018    & \textbf{Tutorial editor}, 
				  \textit{Journal of Mathematical Psychology}\\
2014 -- 2016    & \textbf{Consulting editor}, 
			      \textit{Journal of Mathematical Psychology}\\
\elist

\noindent\textbf{Ad hoc reviewer} for \textit{Acta Psychologica}; \textit{Advances in Methods and Practices in Psychological Science}; \textit{the Annual Meeting of the Society for Cognitive Science (conference)}; \textit{Behavior Research Methods; Clinical Epidemiology}; \textit{Cognition}; \textit{Cognition, Brain, and Behavior}; \textit{Cognitive Psychology}; \textit{Cognitive Science}; \textit{Collabra}; \textit{Decision}; \textit{Entropy}; \textit{Experimental Psychology}; \textit{iPerception}; \textit{Journal of Cognitive Neuroscience}; \textit{Journal of Experimental Psychology: General}; \textit{Journal of Mathematical Psychology}; \textit{Journal of Memory and Language}; \textit{Memory \& Cognition}; \textit{Methodology}; \textit{Perspectives in Psychological Science}; \textit{PLOS ONE}; \textit{Proceedings of the National Academy of Science}; \textit{Psychological Science}; \textit{Psychological Methods}; \textit{Psychological Research}; \textit{Psychological Review}; \textit{Psychometrika}; \textit{Psychonomic Bulletin \& Review}; \textit{Quarterly Journal of Experimental Psychology}; and others.\\

\noindent\textbf{Ad hoc reviewer} for the \textit{European Research Council}; the \textit{Interuniversity Graduate School of Psychometrics and Sociometrics}; the \textit{National Endowment for the Humanities}; the \textit{National Science Foundation}; and others.

\subsection*{Events organized}
\slist
July 2021       & \textbf{Organizer}, ``54th Annual Meeting of the Society for Mathematical Psychology,'' a virtual conference\\
July 2020       & \textbf{Organizer}, ``53rd Annual Meeting of the Society for Mathematical Psychology,'' \sout{Toronto, Ontario} a virtual conference\\
July 2019       & \textbf{Organizer}, ``52nd Annual Meeting of the Society for Mathematical Psychology,'' Montreal, Quebec\\
July 2018       & \textbf{Organizer} (with R.~Shiffrin), ``On the relationship between scientific practice and statistical practice,'' Madison, WI\\
July 2018       & \textbf{Organizer} (with M.~D.~Lee), ``Workshop on robust social science,'' Orlando, FL\\
May 2017        & \textbf{Organizer} (with Z.~Oravecz),
				  ``Models and methods of well-being,'' 
                  Boston, MA\\
November 2016   & \textbf{Organizer} (with A.~H.~Criss and E.-J.~Wagenmakers),
				  ``Computational approaches to cognition,'' 
                  Boston, MA\\
May 2016        & \textbf{Organizer}, ``Cognitive psychometrics in action,'' 
%				   Speakers: Joachim Vandekerckhove, Klaus Oberauer,
%                  Edgar Erdfelder, Dora Matzke.  
                  Chicago, IL\\
November 2015   & \textbf{Organizer} (with A.~H.~Criss and E.-J.~Wagenmakers),
				  ``Mathematical Psychology at Psychonomics,''
                  Chicago, IL\\
July 2015       & \textbf{Organizer}, ``Applications of mathematical
				  psychology to industry meeting,'' 
                  Newport Beach, CA\\
July 2015       & \textbf{Organizer} (with J.~S.~Trueblood), ``48th Annual
				  Meeting of the Society for Mathematical
                  Psychology,'' Newport Beach, CA\\
July 2015       & \textbf{Organizer}, ``Teaching Bayesian statistics with
				  JASP,'' Newport Beach, CA\\
November 2014   & \textbf{Organizer}, ``Using BayesFactor for practical
				  Bayesian analysis.''  
                  %Speakers: Richard Morey and Joachim Vandekerckhove.
                  Irvine, CA\\
March 2014      & \textbf{Organizer}, ``Workshop on recent advances in
				  Bayesian inference.''
                  %Speakers: John Kruschke, Jeffrey Rouder, Mario Perrugia, Hal Stern, Wesley Johnson.
                  Irvine, CA\\
November 2013   & \textbf{Organizer} (with J.~Krichmar and R.~Srinivasan),
				  ``Workshop on interfacing models with brain
                  signals to investigate cognition.''  
                  %Speakers: Will Alexander, Nathaniel Daw, Mimi Liljeholm, David Noelle, Thomas Palmeri, Roger Ratcliff, John Serences, Brandon Turner.
                  Irvine, CA\\
August 2010     & \textbf{Organizer}, ``Practical applications of models for
				  response time.''
                  %Speakers: Joachim Vandekerckhove, Roger Ratcliff, Amy Criss, Fabio Idrobo, Gilles Dutilh, Tiffany Ho, Corey White. 
                  Portland, OR
\elist

\subsection*{Other service to the field}
\slist
  2014   & \textbf{Developer}, ``Minimal frustration'' automated scheduler
           for the 47th Annual Meeting of the Society for
           Mathematical Psychology. 
 \elist



 %\input{includes/research}
 %\input{includes/teaching}

\end{document}
