

	% \newcommand{\vdkh}{\textbf{Vandekerckhove, J.}}
\subsection*{Published work}\srefs
\item[51.] Etz, A., Haaf, J. M., Rouder, J. N., \& \vdkh{} (in press).\newblock Bayesian inference and testing any hypothesis you can specify.\newblock {\em Advances in Methods and Practices in Psychological Science}. Via osf.io/mvp53.% 51

\item[50.] \vdkh{}, Rouder, J. N., \& Kruschke, J. (2018).\newblock Editorial: Bayesian methods for advancing psychological science.\newblock {\em Psychonomic Bulletin and Review, 25,} 1-4. Via osf.io/2es64.% 50

\item[49.] Baribault, B., Donkin, C., Little, D. R., Trueblood, J., Oravecz, Z., van Ravenzwaaij, D., White, C. N., de Boeck, P., \& \vdkh{} (2018).\newblock Metastudies for robust tests of theory.\newblock {\em Proceedings of the National Academy of Sciences, 115,} 2607-2612. Via osf.io/u2vwa.% 49

\item[48.] Dutilh, G., Annis, J., Brown, S. D., Cassey, P., Evans, N. J., Grasman, R. P. P. P., Hawkins, G. E., Heathcote, A., Holmes, W. R., Krypotos, A.-M., Kupitz, C. N., Leite, F. P., Lerche, V., Lin, Y.-S., Logan, G. D., Palmeri, T. J., Starns, J. J., Trueblood, J. S., van Maanen, L., van Ravenzwaaij, D., \vdkh{}, Visser, I., Voss, A., White, C. N., Wiecki, T. V., Rieskamp, J., \& Donkin, C. (in press).\newblock The quality of response time data inference: A blinded, collaborative approach 
                  to the validity of cognitive models.\newblock {\em Psychonomic Bulletin and Review}. Via osf.io/g7ka7.% 48

\item[47.] Heshmati, S., Oravecz, Z., Pressman, S., Batchelder, W. H., Muth, C., \& \vdkh{} (in press).\newblock What does it mean to feel loved? Cultural agreement and individual differences.\newblock {\em Journal of Social and Personal Relationships}. % 47

\item[46.] Rouder, J. N., Haaf, J., \& \vdkh{} (2018).\newblock Bayesian Inference in Psychology, Part IV: Parameter estimation and Bayes factors.\newblock {\em Psychonomic Bulletin and Review, 25,} 102-113. Via osf.io/c53tp.% 46

\item[45.] Matzke, D., Boehm, U., \& \vdkh{} (2018).\newblock Bayesian Inference in Psychology, Part III: Bayesian parameter estimation in nonstandard models.\newblock {\em Psychonomic Bulletin and Review, 25,} 77-101. Via osf.io/ucmaz.% 45

\item[44.] Etz, A., \& \vdkh{} (2018).\newblock Introduction to Bayesian inference for psychology.\newblock {\em Psychonomic Bulletin and Review, 25,} 5-34. Via osf.io/wskex.% 44

\item[43.] Okada, K., \vdkh{}, \& Lee, M. D. (2018).\newblock Modeling when people quit: Bayesian censored geometric models with hierarchical and latent-mixture extensions.\newblock {\em Behavior Research Methods, 50,} 406-415. Via osf.io/v6x8b.% 43

\item[42.] Dutilh, G., \vdkh{}, Ly, A., Matzke, D., Pedroni, A., Frey, R., Rieskamp, J., \& Wagenmakers, E.-J. (2017).\newblock A test of the diffusion model explanation for the Worst Performance Rule using preregistration and blinding.\newblock {\em Attention, Perception, and Performance, 79,} 713-725. Via osf.io/y74g6.% 42

\item[41.] van Ravenzwaaij, D., Donkin, C., \& \vdkh{} (2017).\newblock The EZ diffusion model provides a powerful test of simple empirical effects.\newblock {\em Psychonomic Bulletin and Review, 24,} 547-556. % 41

\item[40.] L\'{u}cio, P. S., Salum, G. A., Rohde, L. A. P., Gadelha, A., Swardfager,  W., \vdkh{}, Pan, P. M., Polanczyk, G., do Ros\'{a}rio, M. C., Jackowski, A. P., Mari, J. d. J., \& and Cogo-Moreira, H. (2017).\newblock Poor stimulus discriminability as a common neuropsychological deficit between ADHD and reading ability in young children: a  moderated mediation model.\newblock {\em Psychological Medicine, 47,} 255-266. % 40

\item[39.] \vdkh{}, \& Wagenmakers, E.-J. (2016).\newblock C. S. Peirce on the Crisis of Confidence and the ``No More Bets'' Heuristic.\newblock {\em The Winnower, 4843.} % 39

\item[38.] Oravecz, Z., Muth, C., \& \vdkh{} (2016).\newblock Do people agree on what makes one feel loved? A cognitive psychometric approach to the consensus on felt love.\newblock {\em PLoS ONE, 11,} e0152803. % 38

\item[37.] Nunez, M. D., \vdkh{}, \& Srinivasan, R. (2017).\newblock How attention influences perceptual decision making: Single-trial EEG correlates of drift-diffusion model parameters.\newblock {\em Journal of Mathematical Psychology, 76B,} 117-130. % 37

\item[36.] Etz, A., \& \vdkh{} (2016).\newblock A Bayesian perspective on the Reproducibility Project: Psychology.\newblock {\em PLoS ONE, 11,} e0149794. % 36

\item[35.] Oravecz, Z., Tuerlinckx, F., \& \vdkh{} (2016).\newblock Bayesian data analysis with the bivariate hierarchical Ornstein-Uhlenbeck process model.\newblock {\em Multivariate Behavioral Research, 51,} 106-119. % 35

\item[34.] Guan, M., \& \vdkh{} (2016).\newblock A Bayesian approach to mitigation of publication bias.\newblock {\em Psychonomic Bulletin and Review, 23,} 74-86. % 34

\item[33.] Van Elk, M., Matzke, D., Gronau, Q., Guan, M., \vdkh{}, \& Wagenmakers, E. J. (2015).\newblock Meta-analyses are no substitute for registered replications: a skeptical perspective on religious priming.\newblock {\em Frontiers in Psychology, 6.} % 33

\item[32.] Kupitz, C., Buschkuehl, M., Jaeggi, S., Jonides, J., Shah, P., \& \vdkh{} (2015).\newblock A diffusion model account of the transfer-of-training effect.\newblock In R. Dale and C. Jennings and P. Maglio and T. Matlock and D. Noelle and A. Warlaumont and J. Yoshimi (Eds.), {\em Proceedings of the 37th Annual Conference of the Cognitive Science Society}. Austin, TX: Cognitive Science Society. % 32

\item[31.] Guan, M., Lee, M. D., \& \vdkh{} (2015).\newblock A hierarchical cognitive threshold model of human decision making on different length optimal stopping problems.\newblock In R. Dale and C. Jennings and P. Maglio and T. Matlock and D. Noelle and A. Warlaumont and J. Yoshimi (Eds.), {\em Proceedings of the 37th Annual Conference of the Cognitive Science Society}. Austin, TX: Cognitive Science Society. % 31

\item[30.] Mistry, P. K, Trueblood, J. S., \vdkh{}, \& Pothos, E. M. (2015).\newblock A latent-mixture quantum probability model of causal reasoning within a Bayesian inference framework.\newblock In R. Dale and C. Jennings and P. Maglio and T. Matlock and D. Noelle and A. Warlaumont and J. Yoshimi (Eds.), {\em Proceedings of the 37th Annual Conference of the Cognitive Science Society}. Austin, TX: Cognitive Science Society. % 30

\item[29.] Oravecz, Z., Huentelman, M., \& \vdkh{} (2016).\newblock Sequential Bayesian updating for Big Data.\newblock In M. Jones (Eds.), {\em Big Data in Cognitive Science: From Methods to Insights} (pp. 13-33). Sussex, UK: Psychology Press (Taylor \& Francis). % 29

\item[28.] Nunez, M. D., Srinivasan, R., \& \vdkh{} (2015).\newblock Individual differences in attention influence perceptual decision making.\newblock {\em Frontiers in Psychology, 6,} 18. % 28

\item[27.] Zhang, S., Lee, M. D., \vdkh{}, Maris, G., \& Wagenmakers, E.-J. (2014).\newblock Time-varying boundaries for diffusion models of decision making and response time.\newblock {\em Frontiers in Psychology, 5,} 1364. % 27

\item[26.] Lee, M. D., Newell, B., \& \vdkh{} (2014).\newblock Modeling the adaptation of search termination in human decision making.\newblock {\em Decision, 1,} 223-251. % 26

\item[25.] Murphy, P. R., \vdkh{}, \& Nieuwenhuis, S. (2014).\newblock Pupil-linked arousal determines variability in perceptual decision making.\newblock {\em PLOS Computational Biology, 10,} e1003854. % 25

\item[24.] \vdkh{} (2014).\newblock A cognitive latent variable model for the simultaneous analysis of behavioral and personality data.\newblock {\em Journal of Mathematical Psychology, 60,} 58-71. % 24

\item[23.] Wiech, K., \vdkh{}, Zaman, J., Tuerlinckx, F., Vlaeyen, J. W. S., \& Tracey, I. (2014).\newblock Influence of prior information on pain involves biased perceptual decision-making.\newblock {\em Current Biology, 24,} R679-R681. % 23

\item[22.] Wabersich, D., \& \vdkh{} (2014).\newblock The RWiener package: an R package providing distribution functions for the Wiener diffusion model.\newblock {\em The R Journal, 6,} 49-56. % 22

\item[21.] Oravecz, Z., \vdkh{}, \& Batchelder, W. H. (2014).\newblock Bayesian Cultural Consensus Theory.\newblock {\em Field Methods, 26,} 207-222. % 21

\item[20.] Salum, G. A., Sergeant, J., Sonuga-Barke, E., \vdkh{}, Gadelha, A., Pan, P. M., Moriyama, T. S., Graeff-Martins, A. S., Gomes de Alvarenga, P., do Ros\'{a}rio, M. C., Manfro, G. G., Polanczyk, G., \& Rohde, L. A. P. (2014).\newblock Mechanisms underpinning inattention and hyperactivity: neurocognitive support for ADHD dimensionality.\newblock {\em Psychological Medicine, 44,} 3189-3201. % 20

\item[19.] \vdkh{}, Matzke, D., \& Wagenmakers, E.-J. (2015).\newblock Model comparison and the principle of parsimony.\newblock In J. R. Busemeyer, J. T. Townsend, Z. J. Wang, and A. Eidels (Eds.), {\em Oxford Handbook of Computational and Mathematical Psychology} (pp. 300-317). Oxford, UK: Oxford University Press. % 19

\item[18.] Wabersich, D., \& \vdkh{} (2014).\newblock Extending JAGS: A tutorial on adding custom distributions to JAGS (with a diffusion model example).\newblock {\em Behavior Research Methods, 46,} 15-28. % 18

\item[17.] Salum, G. A., Sergeant, J., Sonuga-Barke, E., \vdkh{}, Gadelha, A., Pan, P. M., Moriyama, T. S., Graeff-Martins, A. S., Gomes de Alvarenga, P., do Ros\'{a}rio, M. C., Manfro, G. G., Polanczyk, G., \& Rohde, L. A. P. (2014).\newblock Specificity of basic information processing and inhibitory control in attention deficit/hyperactivity disorder.\newblock {\em Psychological Medicine, 44,} 617-631. % 17

\item[16.] \vdkh{}, Guan, M., \& Styrcula, S. (2013).\newblock The consistency test may be too weak to be useful: Its systematic application would not improve effect size estimation in meta-analyses.\newblock {\em Journal of Mathematical Psychology, 57,} 170-173. % 16

\item[15.] Pe, M., \vdkh{}, \& Kuppens, P. (2013).\newblock A diffusion model account of the relationship between the emotional flanker task and depression and rumination.\newblock {\em Emotion, 13,} 739-747. % 15

\item[14.] Dutilh, G., Forstmann, B. U., \vdkh{}, \& Wagenmakers, E.--J. (2013).\newblock A diffusion model account of age differences in posterror slowing.\newblock {\em Psychology and Aging, 28,} 64-76. % 14

\item[13.] Dutilh, G., \vdkh{}, Forstmann, B. U., Keuleers, E., Brysbaert, M., \& Wagenmakers, E.-J. (2012).\newblock Testing theories of post-error slowing.\newblock {\em Attention, Perception, and Psychophysics, 7,} 454-465. % 13

\item[12.] Oravecz, Z., Tuerlinckx, F., \& \vdkh{} (2011).\newblock A hierarchical latent stochastic differential equation model for affective dynamics.\newblock {\em Psychological Methods, 16,} 468-490. % 12

\item[11.] \vdkh{}, Tuerlinckx, F., \& Lee, M. D. (2011).\newblock Hierarchical diffusion models for two-choice response times.\newblock {\em Psychological Methods, 16,} 44-62. % 11

\item[10.] \vdkh{}, Verheyen, S., \& Tuerlinckx, F. (2010).\newblock A crossed random effects diffusion model for speeded semantic categorization data.\newblock {\em Acta Psychologica, 133,} 269-282. % 10

\item[9.] Wetzels, R., \vdkh{}, Tuerlinckx, F., \& Wagenmakers, E.-J. (2010).\newblock Bayesian parameter estimation in the Expectancy Valence model of the Iowa gambling task.\newblock {\em Journal of Mathematical Psychology, 54,} 14-27. % 9

\item[8.] Dutilh, G., \vdkh{}, Tuerlinckx, F., \& Wagenmakers, E.-J. (2009).\newblock A diffusion model decomposition of the practice effect.\newblock {\em Psychonomic Bulletin and Review, 16,} 1026-1036. % 8

\item[7.] Oravecz, Z., Tuerlinckx, F., \& \vdkh{} (2009).\newblock A hierarchical Ornstein-Uhlenbeck model for continuous repeated measurement data.\newblock {\em Psychometrika, 74,} 395-418. % 7

\item[6.] Panis, S., De Winter, J., \vdkh{}, \& Wagemans, J. (2008).\newblock Identification of everyday objects on the basis of fragmented versions of outlines.\newblock {\em Perception, 37,} 271-289. % 6

\item[5.] \vdkh{}, \& Tuerlinckx, F. (2008).\newblock Diffusion Model Analysis with MATLAB: A DMAT Primer.\newblock {\em Behavior Research Methods, 40,} 61-72. % 5

\item[4.] \vdkh{}, Tuerlinckx, F., \& Lee, M. D. (2008).\newblock A Bayesian approach to diffusion process models of decision-making.\newblock In V. M. Sloutsky, B. C. Love, \& K. McRae (Eds.), {\em Proceedings of the 30th Annual Conference of the Cognitive Science Society} (pp. 1429-1434). Austin, TX: Cognitive Science Society. % 4

\item[3.] Spruyt, A., Hermans, D., De Houwer, J., \vdkh{}, \& Eelen, P. (2007).\newblock On the predictive validity of indirect attitude measures: Prediction of consumer choice behavior on the basis of affective priming in the picture-picture naming task.\newblock {\em Journal of Experimental Social Psychology, 43,} 599-610. % 3

\item[2.] \vdkh{}, Panis, S., \& Wagemans, J. (2007).\newblock The concavity effect is a compound of local and global effects.\newblock {\em Perception and Psychophysics, 69,} 1253-1260. % 2

\item[1.] \vdkh{}, \& Tuerlinckx, F. (2007).\newblock Fitting the Ratcliff diffusion model to experimental data.\newblock {\em Psychonomic Bulletin and Review, 14,} 1011-1026. % 1
\erefs


